### 2019-02-12 sections/relatedwork.tex
Added citations to related work

BPEL\todo{cite} is another popular business process language. The standardized
language allows for the specification of actions within business processes,
using an XML format. Processes specified in BEPL are executable, just like YAWL.

@@

If This Then That (IFTTT)\todo{cite} is a web service that allows users to write and
configure simple conditional statements called applets, that can interact with
web services and IoT devices. These applets can be seen as tiny workflows, that
facilitate collaboration between different services and platforms. The
complexity of the flow is very limited however, and is not geared towards humans
collaborating.

@@

Google forms\todo{cite} and Wufoo\todo{cite} are web based survey administration apps that allows
users to compose forms and gather data from them. They are comparable to TOP and
iTasks in that they provide an easy way for users to construct forms on the web.
However, Google forms and Wufoo do not allow users to define what the system
then should do with this information, and can therefore not be regarded as a
workflow or business process modeling systems.

>>>>

BPEL~\cite{bpel} is another popular business process language. The standardized
language allows for the specification of actions within business processes,
using an XML format. Processes specified in BEPL are executable, just like YAWL.

@@

If This Then That (IFTTT)~\cite{IFTTT} is a web service that allows users to write and
configure simple conditional statements called applets, that can interact with
web services and IoT devices. These applets can be seen as tiny workflows, that
facilitate collaboration between different services and platforms. The
complexity of the flow is very limited however, and is not geared towards humans
collaborating.

@@

Google forms~\cite{googleforms} and Wufoo~\cite{wufoo} are web based survey administration apps that allows
users to compose forms and gather data from them. They are comparable to TOP and
iTasks in that they provide an easy way for users to construct forms on the web.
However, Google forms and Wufoo do not allow users to define what the system
then should do with this information, and can therefore not be regarded as a
workflow or business process modeling systems.
